\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-11 k-planar.tex
Pfffft

\note{DW}{I suggest we use consecutive numbering of theorems, lemmas, etc. Theorem 1, Lemma 2, Observation 3, etc.}

\note{DW}{I suggest we delete ``We use $G'\subseteq G$ to denote subgraph containment; that is, $V(G')\subseteq V(G)$ and $E(G')\subseteq E(G)$. '' This is absolutely standard.}

@@

This theorem has applications in diverse areas, including queue layouts  \citep{DJMMUW20}, non-repetitive colouring  \citep{dujmovic.esperet.ea:planar}, $p$-centered colouring  \citep{DFMS21}, and adjacency labelling \citep{DEJGMM21}, which we explore in \cref{Applications}. For example, we prove that $k$-planar graphs have bounded non-repetitive chromatic number (for fixed $k$). Prior to the recent work of \citet{dujmovic.esperet.ea:planar}, it was even open whether planar graphs have bounded non-repetitive chromatic number.

\referee{1}{3. pages 2 – 4: The paragraph following Theorem 2 and Section 1.3
(except for the fact that the apex assumption is necessary) is repetition
of things discussed earlier on in the introduction.}

\note{PM}{Kind of, but I suggest we keep that paragraph and section anyway. Justification: They're both short and they describe the exact bounds for bounded genus graphs, which you don't get from the one-paragraph description in Section~1.0.}

\note{DW}{I suggest we write, ``This theorem has applications in diverse areas, which we explore in \cref{Applications}....''}

@@

  Thus, $a_0,\ldots,a_p$ is a lazy walk in $H^+$ of length $p\le k$ where the distance $s_i$ between $a_i$ and the root $x_0$ of $T$ is non-decreasing.  By removing repeated vertices this gives a path in the directed graph $\overrightarrow{H}^+$ obtained by directing each edge $xy\in E(H^+)$ from its $T$-descendant $x$ towards its $T$-ancestor $y$.
  Finally, we are in a position to appeal to \cite[Lemma~24]{PS21} which states that the number of nodes in $\overrightarrow{H}^+$ that can be reached from any node $x$ by a directed path of length at most $k$ is at most $\binom{k+t}{t}$.

  \note{DW}{replace Lemma~24 by Lemma~13, right?}

>>>>

% \note{DW}{I suggest we use consecutive numbering of theorems, lemmas, etc. Theorem 1, Lemma 2, Observation 3, etc.}

\note{PM}{Agreed. Done.}

% \note{DW}{I suggest we delete ``We use $G'\subseteq G$ to denote subgraph containment; that is, $V(G')\subseteq V(G)$ and $E(G')\subseteq E(G)$. '' This is absolutely standard.}

@@

This theorem has applications in diverse areas, which we explore in \cref{Applications}.

% This theorem has applications in diverse areas, including queue layouts  \citep{DJMMUW20}, non-repetitive colouring  \citep{dujmovic.esperet.ea:planar}, $p$-centered colouring  \citep{DFMS21}, and adjacency labelling \citep{DEJGMM21}, which we explore in \cref{Applications}. For example, we prove that $k$-planar graphs have bounded non-repetitive chromatic number (for fixed $k$). Prior to the recent work of \citet{dujmovic.esperet.ea:planar}, it was even open whether planar graphs have bounded non-repetitive chromatic number.
%
% \referee{1}{3. pages 2 – 4: The paragraph following Theorem 2 and Section 1.3
% (except for the fact that the apex assumption is necessary) is repetition
% of things discussed earlier on in the introduction.}
%
% \note{PM}{Kind of, but I suggest we keep that paragraph and section anyway. Justification: They're both short and they describe the exact bounds for bounded genus graphs, which you don't get from the one-paragraph description in Section~1.0.}
%
% \note{DW}{I suggest we write, ``This theorem has applications in diverse areas, which we explore in \cref{Applications}....''}

@@

  Thus, $a_0,\ldots,a_p$ is a lazy walk in $H^+$ of length $p\le k$ where the distance $s_i$ between $a_i$ and the root $x_0$ of $T$ is non-decreasing.  By removing repeated vertices this gives a path in the directed graph $\overrightarrow{H}^+$ obtained by directing each edge $xy\in E(H^+)$ from its $T$-descendant $x$ towards its $T$-ancestor $y$.
  Finally, we are in a position to appeal to \cite[Lemma~13]{PS21} which states that the number of nodes in $\overrightarrow{H}^+$ that can be reached from any node $x$ by a directed path of length at most $k$ is at most $\binom{k+t}{t}$.

  % \note{DW}{replace Lemma~24 by Lemma~13, right?}
  % \note{PM}{Right. Changed.}
